### 2019-08-27 paper/paper.tex
update todo
paper updates

The next part of the workflow extracts the date features and 
convert the value column into matrix form parameterized by 
the size and stride of the sliding window. The final part joins
 the date features and the value matrix to serve as input to the 
 ML with the output representing the values of the time periods 
 to be predicted ahead of time.

@@

TODO: 
\begin{itemize}
\item add plots
\item add stats output
\item add more examples from docs
\end{itemize}
%\begin{verbatim}
%\bibliographystyle{juliacon}
%\bibliography{ref}
%\end{verbatim}
%When submitting the document source (.tex) file to external
%parties, the ref.bib file should be sent with it.
%\cite{bezanson2017julia}

%\input{bib.tex}

>>>>

For prediction tasks, TSML extracts the date features and 
convert the value column into matrix form parameterized by 
the size and stride of the sliding window. The final part joins
 the date features and the value matrix to serve as input to the 
 ML with the output representing the values of the time periods 
 to be predicted ahead of time.

@@

Setup function to run learners in parallel using distributed computing.
\begin{lstlisting}
function parallelmodel(learners::Dict,
            data::DataFrame;trials=5)
  models=collect(keys(learners))
  ctable=@distributed (vcat) for i=1:trials
    # Split into training and test sets
    Random.seed!(3i)
    (train_ind, test_ind) = 
           holdout(size(data, 1), 0.20)
    acc=@distributed (vcat) for model in models
      res=predict(learners[model],
             data,train_ind,test_ind)
      println("trial ",i,", ",model," => ",
              round(res))
      [model res i]
    end
    acc
  end
  df = ctable |> DataFrame
  rename!(df,:x1=>:model,:x2=>:acc,:x3=>:trial)
  gp=by(df,:model) do x
    DataFrame(mean=mean(x.acc),std=std(x.acc),
              n=length(x.acc)) 
  end
  sort!(gp,:mean,rev=true)
  return gp
end
\end{lstlisting}

We can now benchmark the performance of the different machine learners using a sensor dataset by creating a dictionary of workers from Caret, ScikitLearn, and Julia libraries and call the `parallelmode` function:

\begin{lstlisting}
learners=Dict(
  :jvote_ens=>jvote_ens,:jstack_ens=>jstack_ens,
  :jbest_ens=>jbest_ens,:jrf => jrf,:jada=>jada,
  :jsuper_ens=>jsuper_ens,#:crt_rpart=>caret_rpart,
  :crt_svmlinear=>caret_svmlinear,
  :crt_treebag=>caret_treebag,#:crt_rf=>caret_rf, 
  :skl_knn=>sk_knn,:skl_gb=>sk_gb,
  :skl_extratree=>sk_extratree,
  :sk_rf => sk_rf
);

df = parallelmodel(learners,tsdata;trials=3)
\end{lstlisting}

Figure~\ref{fig:sim}  shows a snapshot of running workers exploiting the distributed library of Julia. There are 8 workers running in parallel over 12 different machine learning classifiers.

\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.8\columnwidth]{sim.png} % requires the graphicx package
   \caption{Sample output running several workers}
   \label{fig:sim}
\end{figure}

\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.6\columnwidth]{results.png} % requires the graphicx package
   \caption{Sample Output in 3 Trials}
   \label{fig:performance}
\end{figure}

TODO: 
\begin{itemize}
\item add plots and tables
\item add threading examples for scalability (buggy)
\item add simulations of different datasets to show general applicability (still doing simulations)
\item add results of simulations: Earthquakes sensor; Electric Devices; car sensors; refrigeration devices; household consumption
\end{itemize}

%\begin{verbatim}
%\bibliographystyle{juliacon}
%\bibliography{ref}
%\end{verbatim}
%When submitting the document source (.tex) file to external
%parties, the ref.bib file should be sent with it.
%\cite{bezanson2017julia}

\input{bib.tex}
